---
title: "Google API Geocoding"
author: "Nour Qweder, Jooyoung Lee, Samia Butt"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true

vignette: >
  %\VignetteIndexEntry{Simulate a RAPI package in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

```{r, include = FALSE}
library(ggmap)
library(leaflet)
library(RAPI)
```


## How to use
```{r installation, eval = FALSE}
devtools::install_github("nourqweder/RAPI", build_vignettes = TRUE)
```


## Introduction
 Before start using this package, `ggmap` and `leaflet` package must be installed in order to plot the result of modelling. This packages is created to provide connection between the Google Geocoding API and the users, so that geo-coordinates can be transformed to address, and address can be transformed to geo-cordinates for more efficient detecting position.  With package `leaflet`, the map is drawn, and a few different display mode can be selected.


```{r, eval = FALSE}
#  https://maps.googleapis.com/maps/api/geocode/json?parameters
```

 As above mentioned, `RAPI` works as a  linker between the users and the Google Geocoding API. 


## Usage Methods

### geocodeBylatlng
 `geocodeBylatlng(latitude, longitude)` This function is used to find a written address with its' latitude and longitude. Using this function connects user to the Google API; Google API responds by providing where the input geo-coordinates corresponds to. Input values must be numeric values.


### getAdressInfoByLocation
 `getAdressInfoByLocation(location)` This function is used to find a geo-coords, which are latitude and longitude of the user-given location. Using this function connects user to the Google API; Google API responds by providing where the input location corresponds to. Input values must be character value.
 


### getInforFromInput
`getInforFromInput(address)` This function produces data frame that contains latitude, longitude, and written address of the user-given address. This function contains `getAdressInfoByLocation()` in it; putting written address in the function will generate geo-coords as embedded function within this has connection to Google API to detect its latitude and longitude. Input values must be character values.




## References 
[Advanced R](http://adv-r.had.co.nz/R5.html)
